Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation

### 2015-07-20 draft3.tex
final1

Producing the SFR, gas mass, stellar mass, and metallicity maps provides enough data to examine and compare the K-S law and the extended Schmidt law. To create the surface density map, we divided the value of each pixel by its area in pc$^2$. We investigated the K-S law and the extended Schmidt law by using pixel by pixel method in the entire galaxy as well as comparing the laws in three elliptical regions, assuming the position angle 38$\degr$, inclination of 77$\degr$ for M31 with distance from the centre of the galaxy the same as the ones described in section~\ref{sec: metal}. As mentioned in section~\ref{sec:data}, since the H$_2$ gas mass map has higher angular resolution and smaller pixel size than the HI gas mass map, our final results have two sets of different pixel sizes. Consequently, any plots with surface density of H$_2$ as a tracer of the gas mass will have more data points.

@@

We took the similar approach for the extended Schmidt law. Figures~\ref{fig:es,all}-~\ref{fig:es,regs,halpha,tot} show the results of the pixel by pixel fitting of the extended Schmidt law. For the extended Schmidt law fitting, we plotted our results in 3D to illustrate the relationship between the surface density of the SFR, the gas mass surface density, and stellar mass density more clearly. In these series of plots, X-axis is the gas mass surface density, either molecular gas (H$_2$), the atomic gas (HI), or the total gas, Y-axis is the SFR(TIR) or SFR(FUV + 24 $\mu$m), and Z-axis is the stellar mass surface density. Shadows of our data on each surface are also plotted, to have a more clear picture of correlations between components. Shadows on the X-Y surface is the same as figure~\ref{fig:ks,all}.

@@

\multicolumn{1}{c}{\multirow{9}{*}{Whole Galaxy}} & TIR               & H$_2$ only & 1.05 & -8.98  & 0.97    & 0.35    & -9.53      \\
 & TIR               & HI only    & 1.19 & -9.69  & 0.79    & 0.75    & -10.56     \\
 & TIR               & Total gas  & 0.82 & -9.84  & 0.51    & 0.56    & -10.40     \\
 & FUV + 24 $\mu$m       & H$_2$ only & 1.16 & -9.36  & 1.15    & 0.25    & -9.74      \\
 & FUV + 24 $\mu$m       & HI only    & 1.19 & -9.96  & 0.81    & 0.61    & -10.62     \\
 & FUV + 24 $\mu$m       & Total gas  & 0.78 & -10.09 & 0.49    & 0.45    & -10.50     \\
 & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.16 & -9.26  & 1.07    & 0.38    & -9.86      \\
 & H$\alpha$ + 24 $\mu$m & HI only    & 0.54 & -9.61  & 0.53    & 0.76    & -10.69     \\
 & H$\alpha$ + 24 $\mu$m & Total gas  & 0.54 & -9.82  & 0.37    & 0.59    & -10.55     \\

@@

\multicolumn{1}{c}{\multirow{9}{*}{R$< 8\kpc$}} & TIR               & H$_2$ only & 1.01 & -8.95  & 0.92    & 0.36    & -6.66      \\
 & TIR               & HI only    & 1.63 & -9.93  & 1.14    & 0.65    & -10.38     \\
 & TIR               & Total gas  & 1.07 & -9.99  & 0.87    & 0.41    & -10.21     \\
 & FUV + 24 $\mu$m       & H$_2$ only & 1.07 & -9.30  & 1.03    & 0.18    & -9.62      \\
 & FUV + 24 $\mu$m       & HI only    & 1.29 & -10.06 & 1.02    & 0.45    & -10.34     \\
 & FUV + 24 $\mu$m       & Total gas  & 0.89 & -10.12 & 0.81    & 0.21    & -10.18      \\
 & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.14 & -9.23  & 1.03    & 0.41    & -6.47      \\
 & H$\alpha$ + 24 $\mu$m & HI only    & 1.29 & -9.56  & 0.96    & 1.54    & -11.10     \\
 & H$\alpha$ + 24 $\mu$m & Total gas  & 0.90 & -9.99  & 0.65    & 1.27    & -10.88    \\

@@

\multicolumn{1}{c}{\multirow{9}{*}{$8\kpc < $R $< 18\kpc$}} & TIR               & H$_2$ only & 1.08 & -8.90  & 1.00    & 0.40    & -9.59      \\
 & TIR               & HI only    & 1.16 & -9.58  & 0.84    & 0.77    & -10.53     \\
 & TIR               & Total gas  & 0.79 & -9.77  & 0.50    & 0.58    & -10.38     \\
 & FUV + 24 $\mu$m       & H$_2$ only & 1.21 & -9.28  & 1.15    & 0.31    & -9.82      \\
 & FUV + 24 $\mu$m       & HI only    & 1.19 & -9.88  & 0.85    & 0.63    & -10.61     \\
 & FUV + 24 $\mu$m       & Total gas  & 0.75 & -10.04 & 0.47    & 0.47    & -10.47     \\
 & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.18 & -9.18  & 1.09    & 0.41    & -9.88      \\
 & H$\alpha$ + 24 $\mu$m & HI only    & 0.56 & -9.49  & 0.72    & 0.81    & -10.67     \\
 & H$\alpha$ + 24 $\mu$m & Total gas  & 0.52 & -9.71  & 0.40    & 0.61    & -10.47  \\

@@

\multicolumn{1}{c}{\multirow{9}{*}{$18\kpc <$ R $\la 25\kpc$}} & TIR               & H$_2$ only & 2.08 & -8.76  & 1.81    & 1.32    & -5.82      \\
 & TIR               & HI only    & 1.30 & -9.68  & 0.83    & 0.78    & -10.54     \\
 & TIR               & Total gas  & 0.86 & -9.83  & 0.55    & 0.57    & -10.38     \\
 & FUV + 24 $\mu$m       & H$_2$ only & 2.87 & -9.18  & 2.89    & 1.49    & -11.33     \\
 & FUV + 24 $\mu$m       & HI only    & 1.27 & -9.95  & 0.85    & 0.64    & -10.63     \\
 & FUV + 24 $\mu$m       & Total gas  & 0.80 & -10.08 & 0.52    & 0.48    & -10.49     \\
 & H$\alpha$ + 24 $\mu$m & H$_2$ only & 2.86 & -9.05  & 3.12    & 1.30    & -10.86     \\
 & H$\alpha$ + 24 $\mu$m & HI only    & 0.63 & -9.62  & 0.44    & 0.81    & -10.62     \\
 & H$\alpha$ + 24 $\mu$m & Total gas  & 0.60 & -9.84  & 0.39    & 0.66    & -10.52     \\

@@

\begin{table*}
\caption{Similar to table~\ref{table:res} but here the fitting performed on the regions with size of 750~pc, and we only showed the results from SFR(FUV+24$\mu$m).}
\label{table:res750}
\begin{tabular}{cccrccrr}
\hline\hline
\multicolumn{1}{c}{\multirow{1}{*}{Region}}  & Gas Tracer & {\it N} & A  & \nprime & $\beta$ & A$^\prime$ \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{Whole Galaxy}}
 & H$_2$ only & 0.32 & -9.91   & 0.27  & 0.41    &  -10.31  \\
 & HI only    & 1.24 & -11.36  & 0.85  & 0.65    & -11.60     \\
 & Total gas  & 0.89 & -9.94 & 0.52    & 0.49    & -10.48     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{R$< 8\kpc$}}
 & H$_2$ only & 0.91 & -9.03  & 0.41   & 0.71   & -9.88      \\
 & HI only    & 1.73 & -10.88 & 1.03    & 1.42    & -10.52     \\
 & Total gas  & 0.88 & -9.94  & 1.45    & 0.83    & -9.11      \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$8\kpc < $R $< 18\kpc$}}
 & H$_2$ only & 0.36 & -9.66  & 0.28    &  0.53   & -10.15       \\
 & HI only    & 1.38 & -11.06 & 1.26    & 0.65    & -11.33     \\
 & Total gas  & 0.80 & -10.00 & 0.72    & 0.53    & -10.17     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $\la 25\kpc$}} 
 & H$_2$ only & 0.34 & -9.47  &  0.34    & 0.75    & -9.72   \\
 & HI only    & 1.46 & -10.73  & 1.05    & 0.84    & -11.44     \\
 & Total gas  & 0.85 & -9.86 & 0.58    & 0.66    & -10.26     \\
 \hline
\end{tabular}
\end{table*}

@@

our results for the whole-galaxy fit of the K-S law show that using total gas gives a sub-linear relation between \sigmasfr and \sigmatotalgas. While, for using the H$_{2}$ only gas or HI only gas we find the nearly super-linear relation. These results are different from power indices estimated by \cite{Ford13}, $N=2.03\pm0.04$ in case of total gas and $N=0.6\pm0.01$ in case of H$_{2}$ only gas. \cite{Tabatabaei10} estimated the K-S law power index $N=1.30\pm0.05$ using the total gas and $N=0.96\pm0.03$ using the H$_{2}$ only gas. The reason behind these differences is mostly because of the statical method we chose. The OLS fitting using H$_{2}$ only gas gives us the power index of $N=0.57\pm1e-4$ which is close to \cite{Ford13} results but still different from the results from \cite{Tabatabaei10} which, could be the same reason \cite{Ford13} suggested for discrepancy between their results and results from \cite{Tabatabaei10}. However, results from the OLS fitting with \sigmatotalgas gives the same results as the fitting with the Bayesian method.% Another differences between our calculation with \cite{Ford13} and \cite{Tabatabaei10} is that both of them used the de-projected values for their calculation which, were calculated by multiplying all of their map by factor of $cos(i)$, inclination angle. We didn't include the calculation of effect of the inclination angle in our results. I checked and my reults doesn't changed

 \cite{Bigiel08} argued that there is no universal relationship between the surface density of the total gas and the SFR. They also showed that the SFR and the molecular hydrogen have a linear relationship. \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indices and all of them are lower than \cite{Bigiel08}. Although some of our results in table`\ref{table: res} showed the nearly linear correlation between the SFR and the molecular hydrogen, we couldn't find any specific trend between power indices in the different regions.

@@

It is well established that metallicity in the centre of M31 is more than the outer disk regions \citep[e.g.][]{Draine14}. Inverse correlation between metallicity and x-factor, which was described in section~\ref{sec:intro} gives the underestimation of the power indices from fitting the K-S law in the case of the molecular gas only and total gas. Thus power index of the K-S law is more closer to the original suggestion for the KS law ($\lt N \sim 1.56$). Moreover, results of \cite{Krumholz09} showed that a correlation between SFR and metallicity is strongly depends on amount of total gas in galaxies. We could not see any correlation between the SFR and metallicity in sub-kiloparces regions~\ref{fig:metal}. We estimated the SFR using \cite{Krumholz09} star formation rate for regions with size of $\sim$750~pc. We found that the SFR calculated using Krumholz law in average 45$\%$ different from the measured SFR. We used an average value of metallicity 1.65, clumping factor of 1.2 to get this results. A through calculation is needed to solve the issue of this controversy which is beyond scope of this paper.

 \cite{Mannucci10} and \cite{Lilly13} assumed the K-S law holds for their sample of study and obtained a correlation between, metallicity and the stellar mass, the gas mass and the SFR. They found that increasing both the SFR and the stellar mass increases metallicity, but increasing the gas mass decreases metallicity (equation 9 in \citep{Mannucci10}). However, by considering results from \cite{wong13} regarding the dependency of rate of HI-H$_2$ conversion to metallicity, \cite{Roychowdhury15} showed that the KS law is independent of metallicity in galaxies with HI as a dominant gas. As demonstrated in ~\ref{fig:metal}, we plot metallicity versus the SFR and the stellar mass, and could not find any correlation.

\begin{figure*}
    \centering
    \begin{subfigure}[b]{053\textwidth}
        \centering
        \includegraphics[width=\textwidth]{metal_vs_sfr.png}
        \caption{SFR(FUV + 24 $\mu$m) vs matalicity surface density}
        \label{fig:mtal_sfr}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{metal_vs_star.png}
        \caption{Stellar mass vs metalicity surface density}
        \label{fig:metal_star}}
    \end{subfigure}
    \caption{Right: the SFR(FUV + 24 $\mu$m) surface density versus metalicity surface density and left: Stellar mass vs metalicity surface density  shows the stellar mass. Each point shows a region with size of $\sim$750~pc. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
    \label{fig:metal}
\end{figure*}

%----------------------------------------------------------------------------------------
%SUMMERY
%----------------------------------------------------------------------------------------
\section{Summary}
 We investigated the K-S law, the extended Schmidt law and the Krumholz law in both global and local scales in M31. We have determined surface density of star formation rate, gas mass and the stellar mass of this galaxy. We produced three SFR maps in M31. The first uses a combination of the FUV and 24 \um emission. For the second SFR map, we used a combination of the H$\alpha$ and 24 \um emission, and the third one was produced using total-infrared luminosity. We noticed that H$_\alpha$ data available for M31 is not suitable for SFR study ~\ref{app:halpha}. We calculated the total SFR from FUV and 24 \um emission is 0.31$\pm$ 0.04 M$_{\odot}$yr$^{-1}$. We also produced the ISM map, using molecular gas only, atomic gas only and the total gas.

1) We found the power index of the K-S law is mostly depended on which gas we use as a tracer of the gas mass in galaxy. And it is mostly independent of the SFR tracer.

2) We showed that, using different fitting methods gives us different results

3) Our results showed although there is a correlation between \sigmasfr and \sigmagas, it is not the same in all regions in M31.

4) We confirmed \cite{Shi11} suggestions that the surface density of stars has impact on the SFR, and in regions with law gas surface brightness this impact is even more important.

5) We could not find any relation between SFR and metallicity.

>>>>

Producing the SFR, gas mass, stellar mass, and metallicity maps provides enough data to examine and compare the K-S law and the extended Schmidt law. To create the surface density map, we divided the value of each pixel by its area in pc$^2$. We investigated the K-S law and the extended Schmidt law by using pixel by pixel method in the entire galaxy as well as comparing the laws in three elliptical regions, assuming the position angle 38$\degr$, inclination of 77$\degr$ for M31 with distance from the centre of the galaxy the same as the ones described in section~\ref{sec:metal}. As mentioned in section~\ref{sec:data}, since the H$_2$ gas mass map has higher angular resolution and smaller pixel size than the HI gas mass map, our final results have two sets of different pixel sizes. Consequently, any plots with surface density of H$_2$ as a tracer of the gas mass will have more data points.

@@

We took the similar approach for the extended Schmidt law. Figures~\ref{fig:es,all}-~\ref{fig:es,regs,fuv,tot} show the results of the pixel by pixel fitting of the extended Schmidt law. For the extended Schmidt law fitting, we plotted our results in 3D to illustrate the relationship between the surface density of the SFR, the gas mass surface density, and stellar mass density more clearly. In these series of plots, X-axis is the gas mass surface density, either molecular gas (H$_2$), the atomic gas (HI), or the total gas, Y-axis is the SFR(TIR) or SFR(FUV + 24 $\mu$m), and Z-axis is the stellar mass surface density. Shadows of our data on each surface are also plotted, to have a more clear picture of correlations between components. Shadows on the X-Y surface is the same as figure~\ref{fig:ks,all}.

@@

\multicolumn{1}{c}{\multirow{9}{*}{Whole Galaxy}} & TIR  & H$_2$ only & 1.02 - 1.05 & -8.99 - -8.98  & 0.93 - 0.97    & 0.33 - 0.35    & -9.56 - -9.53  \\
 & TIR               & HI only    & 1.13 - 1.19 & -9.71 - -9.69  & 0.76 - 0.79    & 0.74 - 0.75    & -10.58 - -10.56     \\
 & TIR               & Total gas  & 0.80 - 0.82 & -9.86 - -9.84  & 0.50 - 0.51    & 0.54 - 0.56    & -10.42 - -10.40     \\
 & FUV + 24 $\mu$m       & H$_2$ only & 1.11 - 1.16 & -9.37-9.36  & 1.06 - 1.15   & 0.23 - 0.25    & -9.78 - -9.74      \\
 & FUV + 24 $\mu$m       & HI only    & 1.16 - 1.19 & -9.97 - -9.96  & 0.78 - 0.81    & 0.59 - 0.61   & -10.64 - -10.62     \\
 & FUV + 24 $\mu$m       & Total gas  & 0.76 - 0.78 & -10.10 - -10.09 & 0.47 - 0.49    & 0.44 - 0.45    & -10.52 - -10.50     \\
 & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.11 - 1.16 & -9.27- -9.26  & 1.02 - 1.07    & 0.36 - 0.38    & -9.89 - -9.86      \\
 & H$\alpha$ + 24 $\mu$m & HI only    & 0.46 - 0.54 & -9.64 - -9.61  & 048 - 0.53    & 0.72 - 0.76    & -10.75 -10.69     \\
 & H$\alpha$ + 24 $\mu$m & Total gas  & 0.50 - 0.54 & -9.85 - -9.82  & 0.34 - 0.37    & 0.55 - 0.59    & -10.61 - -10.55     \\

@@

\multicolumn{1}{c}{\multirow{9}{*}{R$< 8\kpc$}} & TIR & H$_2$ only & 0.94-1.01 & -8.97 - -8.95  & 0.87 - 0.92    & 0.30 - 0.36    & -9.49 - -6.66 \\
 & TIR               & HI only    & 1.31 - 1.63 & -10.00 - -9.93  & 0.84 - 1.14    & 0.48 - 0.65    & -10.55 - -10.38     \\
 & TIR               & Total gas  & 0.92 - 1.07 & -10.10 - -9.99  & 0.80 - 0.87    & 0.24 - 0.41    & -10.37 - -10.21     \\
 & FUV + 24 $\mu$m       & H$_2$ only & 1.00 - 1.07 & -9.32 - -9.30  & 0.95 - 1.03  & 0.15 - 0.18  & -9.68 - -9.62      \\
 & FUV + 24 $\mu$m       & HI only    & 1.11 - 1.29 & -10.10 - -10.06 & 0.78 - 1.02    & 0.29 - 0.45   & -10.49 - -10.34     \\
 & FUV + 24 $\mu$m       & Total gas  & 0.78 - 0.89 &-10.20 - -10.12 & 0.66 - 0.81    & 0.05 - 0.21    & -10.32 - -10.18      \\
 & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.06 - 1.14 & -9.25 - -9.23  & 0.97 - 1.03    & 0.36 - 0.41    & -9.86 - -6.47      \\
 & H$\alpha$ + 24 $\mu$m & HI only    & 0.31 - 1.29 & -9.10 - -9.56  & 0.21 - 0.96    & 0.90 - 1.54    & -12.01 - -11.10     \\
 & H$\alpha$ + 24 $\mu$m & Total gas  & 0.49 - 0.90 & -10.30 - -9.99  & 0.28 - 0.65    & 0.62 - 1.27    & -11.71 - -10.88    \\

@@

\multicolumn{1}{c}{\multirow{9}{*}{$8\kpc < $R $< 18\kpc$}} & TIR & H$_2$ only & 1.04 - 1.08 & -8.91- -8.90 & 0.95 - 1.00 & 0.38 - 0.40 & -9.92 - -9.59 \\
 & TIR               & HI only    & 0.97 - 1.16 & -9.64 - -9.58  & 0.72 - 0.84    & 0.72 - 0.77    & -10.61 - -10.53     \\
 & TIR               & Total gas  & 0.71 - 0.79 & -9.83 - -9.77  & 0.45 - 0.50    & 0.53 - 0.58    & -10.45 - -10.38     \\
 & FUV + 24 $\mu$m       & H$_2$ only & 1.16 - 1.21 & -9.30 - -9.28  & 1.10 - 1.15    & 0.28 - 0.31    & -9.86 - -9.82      \\
 & FUV + 24 $\mu$m       & HI only    & 1.07 - 1.19 & -9.92 - -9.88  & 0.76 - 0.85    & 0.56 - 0.63    & -10.68 - -10.61     \\
 & FUV + 24 $\mu$m       & Total gas  & 0.69 - 0.75 & -10.10 - -10.04 & 0.42 - 0.47    & 0.42 - 0.47    & -10.55 - -10.47     \\
 & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.12 - 1.18 & -9.19 - -9.18  & 1.04 - 1.09    & 0.39 - 0.41    & -9.93 - -9.88      \\
 & H$\alpha$ + 24 $\mu$m & HI only    & 0.33 - 0.56 & -9.95 - -9.49  & 0.57 - 0.72    & 0.70 - 0.81    & -10.85 -10.67     \\
 & H$\alpha$ + 24 $\mu$m & Total gas  & 0.42 - 0.52 & -9.79 - -9.71  & 0.32 - 0.40    & 0.51 - 0.61    & -10.63 - -10.47  \\

@@

\multicolumn{1}{c}{\multirow{9}{*}{$18\kpc <$ R $\la 25\kpc$}} & TIR & H$_2$ only & 1.42 - 2.08 &-8.87- -8.76 & 1.25 - 1.81& 1.20 - 1.32& -10.72 - -5.82 \\
 & TIR               & HI only    & 1.11 - 1.30 & -9.74 - -9.68  & 0.71 - 0.83    & 0.72 - 0.78    & -10.63 - -10.54     \\
 & TIR               & Total gas  & 0.79 - 0.86 &  -9.88 - -9.83  & 0.50 - 0.55    & 0.51 - 0.57    & -10.45 - -10.38     \\
 & FUV + 24 $\mu$m       & H$_2$ only & 1.93 - 2.87 & -9.32 - -9.18  & 1.60 - 2.89    & 1.26 - 1.49& -11.72 - -11.33     \\
 & FUV + 24 $\mu$m       & HI only    & 1.15 - 1.27 & -9.99 - -9.95  & 0.75 - 0.85    & 0.59 - 0.64    & -10.70 - -10.63     \\
 & FUV + 24 $\mu$m       & Total gas  & 0.74 - 0.80 & -10.10 - -10.08 & 0.46 - 0.52    & 0.42 - 0.48    & -10.56 - -10.49     \\
 & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.76 - 2.86 & -9.20- -9.05  & 1.55 - 3.12    & 1.06 - 1.30    & -11.33 - -10.86     \\
 & H$\alpha$ + 24 $\mu$m & HI only    & 0.36 - 0.63 &  -9.71 - -9.62  & 0.23 - 0.44    & 0.69 - 0.81    & -10.80 - -10.62     \\
 & H$\alpha$ + 24 $\mu$m & Total gas  & 0.49 - 0.60 & -9.39 - -9.84  & 0.28 - 0.39    & 0.53 - 0.66    & -10.70 - -10.52     \\

@@

\begin{table*}
\caption{Similar to table~\ref{table:res} but here the fitting performed on the regions with size of 750~pc, and we only showed the results from SFR(FUV+24$\mu$m).}
\label{table:res750}
\begin{tabular}{cccrccrr}
\hline\hline
\multicolumn{1}{c}{\multirow{1}{*}{Region}}  & Gas Tracer & {\it N} & A  & \nprime & $\beta$ & A$^\prime$ \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{Whole Galaxy}}
 & H$_2$ only & 0.26 - 0.32 & -10.00 - -9.91   & 0.22 - 0.27  & 0.27 - 0.41    & -10.52 - -10.31  \\
 & HI only    & 1.08 - 1.24 & -11.60 - -11.36  & 0.73 - 0.85  & 0.58 - 0.65    & -11.78 - -11.60     \\
 & Total gas  & 0.73 - 0.89 & -10.10 - -9.94 & 0.44 - 0.52    & 0.41 - 0.49    & -10.57 - -10.48     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{R$< 8\kpc$}}
 & H$_2$ only & 0.10 - 0.91 & -11.19 - -9.03  & 0.20 - 0.41   & 0.24 - 0.71   & -9.73 - -9.88      \\
 & HI only    & 0.74 - 1.73 & -12.04 - -10.88 & 0.11 - 1.04    & 0.64 - 1.40    & -11.32 - -10.54     \\
 & Total gas  & 0.51 - 0.88 & -10.20 - -9.94  & 0.91 - 1.47    & 0.24 - 0.91    & -9.71 - -9.10      \\%????
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$8\kpc < $R $< 18\kpc$}}
 & H$_2$ only & 0.17 - 0.36 & -10.00 - -9.66  & 0.13 - 0.28    &  0.21 - 0.53   & -10.70 - -10.15       \\
 & HI only    & 0.88 - 1.38 & -11.80 - -11.06 & 0.66 - 1.26    & 0.16 - 0.65    & -12.14 - -11.33     \\
 & Total gas  & 0.55 - 0.80 & -10.20 - -10.00 & 0.41 - 0.72    & 0.08 - 0.53    & -10.72 - -10.17     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $\la 25\kpc$}} 
 & H$_2$ only & 0.11 - 0.34 & -9.95 - -9.47  & 0.19 - 0.34    & 0.24 - 0.75    & -10.64 - -9.72   \\
 & HI only    & 0.76 - 1.46 & -11.80 - -10.73  & 0.60 - 1.05    & 0.55 - 0.84    & -12.02 -11.44     \\
 & Total gas  & 0.52 - 0.85 & -10.10 - -9.86 & 0.28 - 0.58    & 0.30 - 0.65    & -10.75 - -10.26     \\
 \hline
\end{tabular}
\end{table*}

@@

our results for the whole-galaxy fit of the K-S law show that using total gas gives a sub-linear relation between \sigmasfr and \sigmatotalgas. While, for using the H$_{2}$ only gas or HI only gas we find the nearly super-linear relation. These results are different from power indices estimated by \cite{Ford13}, $N=2.03\pm0.04$ in case of total gas and $N=0.6\pm0.01$ in case of H$_{2}$ only gas. \cite{Tabatabaei10} estimated the K-S law power index $N=1.30\pm0.05$ using the total gas and $N=0.96\pm0.03$ using the H$_{2}$ only gas. The reason behind these differences is mostly because of the statical method we chose. The OLS fitting using H$_{2}$ only gas gives us the power index of $N=0.57\pm1e-4$ which is close to \cite{Ford13} results but still different from the results from \cite{Tabatabaei10} which, could be the same reason \cite{Ford13} suggested for discrepancy between their results and results from \cite{Tabatabaei10}. However, results from the OLS fitting with \sigmatotalgas gives the same results as the fitting with the Bayesian method.% Another differences between our calculation with \cite{Ford13} and \cite{Tabatabaei10} is that both of them used the de-projected values for their calculation which, were calculated by multiplying all of their map by factor of $cos(i)$, inclination angle. We didn't include the calculation of effect of the inclination angle in our results.
%%%% Sahar:I checked and my reults doesn't changed

 \cite{Bigiel08} argued that there is no universal relationship between the surface density of the total gas and the SFR. They also showed that the SFR and the molecular hydrogen have a linear relationship. \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indices and all of them are lower than \cite{Bigiel08}. Although some of our results in table`\ref{table:res} showed the nearly linear correlation between the SFR and the molecular hydrogen, we couldn't find any specific trend between power indices in the different regions.

@@

It is well established that metallicity in the centre of M31 is more than the outer disk regions \citep[e.g.][]{Draine14}. Inverse correlation between metallicity and x-factor, which was described in section~\ref{sec:intro} gives the underestimation of the power indices from fitting the K-S law in the case of the molecular gas only and total gas. Thus the calculated power index of the K-S law is more than we showed in table~\ref{table:res}. Another correlation between components of the SFR laws and metalicity was introduced by \cite{Krumholz09}. They found a new SFR law based on a correlation between SFR and metalicity, and suggested that this correlation is strongly depends on amount of total gas in galaxies. We estimated the SFR using \cite{Krumholz09} SFR laws for regions with size of $\sim$750~pc. Using the mid value of metallicity, 1.65, and clumping factor of 1.2, We found that the SFR calculated using Krumholz law in average 45$\%$ different from the measured SFR(FUV + 24 $\mu$m) in this work. %Another way to talk about this law is to show the equation and introduced all the factors and adding that we used it and found this result! .

In more recent studies, \cite{Mannucci10} and \cite{Lilly13} assumed the K-S law holds for their sample of local and high-redshift galaxies and obtained a correlation between, metallicity and the stellar mass, the gas mass and the SFR. They found that increasing both the SFR and the stellar mass increases metallicity, but increasing the gas mass decreases metallicity (equation 9 in \citep{Mannucci10}). However, by considering results from \cite{wong13} regarding the dependency of rate of HI-H$_2$ conversion to metallicity, \cite{Roychowdhury15} showed that the KS law is independent of metallicity in galaxies with HI as a dominant gas. As demonstrated in ~\ref{fig:metal}, we plot metallicity versus the SFR(FUV + 24 $\mu$m) and the stellar mass, and could not find any correlation. We also calculated the Pearson correlation coefficient between metallicity and the SFR, and metallicity and the stellar mass to be 0.07 and 0.04, which confirmed that there is no correlation between metallicity and neither the SFR  nor the stellar mass. Although, we could not find any direct correlation between the SFR and metallicity, we should note that effect of the metallicity on SF laws is ambiguous and more high resolution data is needed to complete this puzzle.

\begin{figure*}
\centering
\includegraphics[width=162mm]{metal12.png}
    \caption{Right: the SFR(FUV + 24 $\mu$m) surface density versus metalicity surface density and left: Stellar mass vs metalicity surface density  shows the stellar mass. Each point shows a region with size of $\sim$750~pc. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
    \label{fig:metal}
\end{figure*}

%----------------------------------------------------------------------------------------
%SUMMERY
%----------------------------------------------------------------------------------------
\section{Summary}
 We investigated the K-S law, the extended Schmidt law and the Krumholz law in both global and local scales in M31. We have determined surface density of star formation rate, gas mass and the stellar mass of this galaxy. We produced three SFR maps in M31. The first uses a combination of the FUV and 24 \um emission. For the second SFR map, we used a combination of the H$\alpha$ and 24 \um emission, and the third one was produced using total-infrared luminosity. We noticed that H$_\alpha$ data available for M31 is not suitable for SFR study ~\ref{app:halpha}. We calculated the total SFR from FUV and 24 \um emission is 0.31$\pm$ 0.04 M$_{\odot}$yr$^{-1}$. We also produced the ISM map, using molecular gas only, atomic gas only and the total gas.
\newline
1) We found the power index of the K-S law is mostly depended on which gas we use as a tracer of the gas mass in galaxy. And it is mostly independent of the SFR tracer.
\newline
2) We showed that, using different fitting methods gives us different results
\newline
3) Our results showed although there is a correlation between \sigmasfr and \sigmagas, it is not the same in all regions in M31. 
\newline
4) We confirmed \cite{Shi11} suggestions that the surface density of stars has impact on the SFR, and in regions with law gas surface brightness this impact is even more important. 
\newline
5) We performed statistical tests to find any correlation between the SFR, or the stellar mass surface density and metallicity, and we could not find any.
\newline
Obtaining images with higher resolution and maps with better coverage of this galaxy will enable us to continue these studies in finer details and will enhance our chances of discovering new star forming regions and novel phenomena.
